Three objections to a novel paradigm in social media effects research

### 2022-07-15 ms.Rmd
Commit manuscript pdf

---
title: Three objections to a novel paradigm in social media effects research
shorttitle: Three objections
leftheader: Three objections
author: 
  - name: Matti Vuorre
    affiliation: 1
    corresponding: yes    # Define only one corresponding author
    address: Oxford Internet Institute, University of Oxford
    email: matti.vuorre@oii.ox.ac.uk
    role:
      - Conceptualization
      - Formal analysis
      - Software
      - Visualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name: Niklas Johannes
    affiliation: 1
    address: Oxford Internet Institute, University of Oxford
    email: niklas.johannes@oii.ox.ac.uk
    role:
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name: Andrew K. Przybylski
    affiliation: 1
    address: Oxford Internet Institute, University of Oxford
    email: andy.przybylski@oii.ox.ac.uk
    role:
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
affiliation:
  - id: 1
    institution: Oxford Internet Institute, University of Oxford
authornote: |
  A non-peer reviewed pre-print of this work is available at <psyarxiv>.
  All code supporting this manuscript is available at <https://github.com/digital-wellbeing/paradigm-comments>.
abstract: |
  The study of social media effects on psychological well-being has reached an impasse: Popular commentators confidently assert that social media are bad for users but research results are mixed and have had little practical impact. In response, one research group has proposed a path forward for the field that moves beyond studying population averages to find effects that are specific to individuals.

>>>>

---
title: Three objections to a novel paradigm in social media effects research
shorttitle: Three objections
leftheader: Three objections
author: 
  - name: Matti Vuorre
    affiliation: 1
    corresponding: yes    # Define only one corresponding author
    address: Oxford Internet Institute, University of Oxford
    email: matti.vuorre@oii.ox.ac.uk
    role:
      - Conceptualization
      - Formal analysis
      - Software
      - Visualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name: Niklas Johannes
    affiliation: 1
    address: Oxford Internet Institute, University of Oxford
    email: niklas.johannes@oii.ox.ac.uk
    role:
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name: Andrew K. Przybylski
    affiliation: 1
    address: Oxford Internet Institute, University of Oxford
    email: andy.przybylski@oii.ox.ac.uk
    role:
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
affiliation:
  - id: 1
    institution: Oxford Internet Institute, University of Oxford
authornote: |
  A non-peer reviewed pre-print of this work is available at <https://psyarxiv.com/dpuya>.
  All code supporting this manuscript is available at <https://github.com/digital-wellbeing/paradigm-comments>.
abstract: |
  The study of social media effects on psychological well-being has reached an impasse: Popular commentators confidently assert that social media are bad for users but research results are mixed and have had little practical impact. In response, one research group has proposed a path forward for the field that moves beyond studying population averages to find effects that are specific to individuals.
